%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Calum}{Brookes}{ \urlstyle{same}\url{http://linkedin.com/in/calumbrookes} \\
\href{mailto:calum.brookes@bbc.co.uk}{calum.brookes@bbc.co.uk} | 07930435754
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Salford}
\descript{BSc Broadcast Engineering}
\location{First Class Honours}

\subsection{Birm. City University}
\descript{MSc Broadcast Engineering}
\location{Distinction}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Languages:}
Java \textbullet{} Bash \textbullet{} Python \textbullet{} LaTeX\ \\ 
Matlab \textbullet{} C \textbullet{} C++ \textbullet{} SQL \\
\sectionsep

\subsection{Engineering}
\location{Interested Fields:}
Service Management \\
Workflow Improvement \\
Incident Management \\
Project Engineering \\
Requirements Assessment \\ 
Technical Documentation \\
IP Infrastructure \\
Broadcast Hardware \\
TV \& Radio Distribution \\
Broadcast Automation \\
Systems Integration \\
Control Software Dev (BNCS) \\
Virtualisation Technologies \\
Monitoring Tools (Icinga/Nagios)\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Courses}
\subsection{Traineeship}
Studio \& Broadcast Technology \\
Digital Workflow Technologies \\
Research Methods \\
Coding \& Digital Signal Processing \\
\sectionsep

\subsection{Apprenticeship}
Cisco CCNA Syllabus \\
Transmission Technologies \\
SQL Databases \\
Practical Programming \& CGI\\
Systems Integration \& Workflow Development \\
Codecs \& Standards \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Employment \& Voluntary Work}

\runsubsection{BBC}
\descript{| Operations Engineer (3 Years)}
\location{Jun 2018 – Present | Glasgow, Scotland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Based in BBC Scotland with Engineering Operations, supporting operations across TV, Radio and building \& facility infrastructure at sites across Scotland.
\item Project work - worked to build new edit faciltiies at Dumbarton studios, VO booths in TV Presentation and upgrading DAW spaces in Pacific Quay.
\item Operational work - 1st line work supporting a 7x20 shift pattern of incident management cover as well as taking on responsibility of 2nd and 3rd line work.
\item Taken primary system ownership for supporting and developing a number of systems in BBC Scotland including the internal Raven ingest/playout system.
\item Worked with key industry suppliers and partners such as Grass Valley, Viz and VCS to find resolutions to incidents which require supplier intervention. 
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Project Manager (1 Year)}
\location{Jan 2020 – Jan 2021 | Glasgow, Scotland}
\begin{tightemize}
\item Undertook a year-long secondment to BBC Scotland PMO.
\item Managed the upgrade of the VCS radio prod \& playout system within Scotland, a multi-site, pan-BBC service upgrade - liasing between local prod teams, BBC suppliers, and local \& national engineering support.
\item Other projects include managing the design, tender \& procurement of the £180,000 studio infrastructure upgrade across the 3 major Pacific Quay TV studios from an established BBC supplier.
\item Returned to ops-supporting projects during COVID - I designed, transferred \& implemented a number of knowledge management services for use within eng support in BBC Scotland - from procurement \& infosec approval of an enterprise Password Manager to be offered as a service in BBC Scotland, migrating knowledge from an old wiki to the BBC's "Confluence" managed service, \& developing our documentation to match our support model.
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Trainee Broadcast Engineer (2 Years)}
\location{Jul 2016 – May 2018 | Glasgow, Scotland}
\begin{tightemize}
\item Based in BBC Scotland with Production Technology Development.
\item Attachment to BBC South West (Plymouth) working in operational support.
\item GE2017 - Guaranteed the IP Video \& Comms service from the Emirates Arena.
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Apprentice Broadcast Engineer (3 Years)}
\location{Sep 2013 – Jul 2016 | Birmingham, England \& Glasgow, Scotland}
\begin{tightemize}
\item Worked as a 3rd line engineer for English Regions' testing and development team, including with the project team releasing ViLoR to English Regions
\item Supported local TV \& radio operations in England and was part of the team that won an RTS Midlands award for "Best News Programme".
\item Secondment to Arqiva \& changed the Radio 4 Long Wave antenna at Droitwich.
\item Was part of the GE and Referendum staff for two General Elections, a Scottish GE and two referendums, as well as the Commonwealth Games.
\item BEng dissertation was to write and support production-facing software services for the Scottish General Election teams.
\end{tightemize}
\sectionsep

\runsubsection{National Student Television Association (2 Years)}
\descript{| Technical Officer }
\location{Jul 2012 – Jul 2014 | UK Nationwide}
\begin{tightemize}
\item Elected \& re-elected for two terms of office.
\item Deployed a total redesign of the association's website \& streaming platform.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}
