%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Calum}{Brookes}{ \urlstyle{same}\url{http://linkedin.com/in/calumbrookes} \\
\href{mailto:calum.brookes@bbc.co.uk}{calum.brookes@bbc.co.uk} | 07930435754
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Salford}
\descript{BSc Broadcast Engineering}
\location{First Class Honours}

\subsection{Birm. City University}
\descript{MSc Broadcast Engineering}
\location{Distinction - Expected June 2018}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Courses}
\subsection{Traineeship}
Studio \& Broadcast Technology \\
Digital Workflow Technologies \\
Research Methods \\
Coding \& Digital Signal Processing \\
\sectionsep

\subsection{Apprenticeship}
Cisco CCNA Syllabus \\
Transmission Technologies \\
SQL Databases \\
Practical Programming \& CGI\\
Systems Integration \& Workflow Development \\
Codecs \& Standards \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Languages:}
Java \textbullet{} Bash \textbullet{} Python \textbullet{} LaTeX\ \\ 
Matlab \textbullet{} C \textbullet{} C++ \textbullet{} SQL \\
\sectionsep

\subsection{Engineering}
\location{Languages:}
Project Engineering \\
Requirements Assessment \\ 
Technical Documentation \\
IP Infrastructure \\
Broadcast Hardware \\
TV \& Radio Distribution \\
Broadcast Automation \\
Workflow Improvement \\
Systems Integration \\
Control Software Dev (BNCS) \\
Monitoring Tools (Icinga/Nagios)\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Employment \& Voluntary Work}

\runsubsection{BBC}
\descript{| Trainee Broadcast Engineer (1 Year)}
\location{Jun 2018 – Present | Glasgow, Scotland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Based in BBC Scotland with Engineering Operations.
\item Working supporting operations across TV, Radio and building \& facility infrastructure at sites across Scotland.
\item Project work - worked to build new edit faciltiies at Dumbarton studios, VO booths in TV Presentation and upgrading DAW spaces in Pacific Quay.
\item Operational work - 1st line work supporting a 7x20 shift pattern incident cover as well as taking on responsibility of 2nd line work supporting a number of systems.
\item Taken primary system ownership for supporting and developing a number of systems in BBC Scotland including the internal Raven ingest/playout system.
\item Worked with key industry suppliers and partners such as Grass Valley, Viz and VCS to find resolutions to incidents which require supplier intervention. 
\item Trained in Autocad and have worked to improve the content of several areas of documentation and knowledge management.
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Trainee Broadcast Engineer (2 Years)}
\location{Jul 2016 – May 2018 | Glasgow, Scotland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Based in BBC Scotland with Production Technology Development.
\item Attachment to BBC South West (Plymouth) working on an AV suite project \& frontline support.
\item GE2017 - Guaranteed the IP Video \& Communications circuits from the Emirates Arena OB.
\item Accepted, installed and tested a camera streaming platform where users can stream QOS protected MPEG video directly from their camera to BBC Pacific Quay without additional equipment.
\item Attended IBC 2017.
\item Commissioned an action replay service for Scottish Prem. Football coverage.
\item MSc - Currently delivering an automated streaming distribution installation for the Scottish Symphony Orchestra.
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Apprentice Broadcast Engineer (3 Years)}
\location{Sep 2013 – Jul 2016 | Birmingham, England \& Glasgow, Scotland}
\begin{tightemize}
\item Worked as a 3rd line engineer for English Regions' testing and dev team.
\item Worked alongside the project team responsible for releasing ViLoR to English Regions.
\item Supported local TV \& radio operations in England, both as an SNG engineer and as a studio support engineer.
\item Was part of the team that won an RTS Midlands award for "Best News Programme".
\item Changed the Radio 4 Long Wave antenna at Droitwich.
\item Was part of the GE and Referendum staff for two General Elections, a Scottish GE and two referendums.
\item Supported OB trucks at the Commonwealth Games and, Hogmanay 2013 and 2014.
\item Worked on two secondments to London and Cardiff's Master Control Rooms.
\item Attended IBC2015.
\item BEng dissertation was to write production-facing software for the Scottish General Election, which was developed quickly and as lean as possible using an agile process.
\end{tightemize}
\sectionsep

\runsubsection{National Student Television Association (2 Years)}
\descript{| Technical Officer }
\location{Jul 2012 – Jul 2014 | UK National}
\begin{tightemize}
\item Elected for two terms of office.
\item Deployed a total redesign of the association's website \& streaming platform.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}
