%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Calum}{Brookes}{ \urlstyle{same}\url{http://linkedin.com/in/calumbrookes} \\
\href{mailto:calum.brookes@bbc.co.uk}{calum.brookes@bbc.co.uk} | 07930435754
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Salford}
\descript{BEng Broadcast Engineering}
\location{First Class Honours}
\sectionsep
\subsection{Birm. City University}
\descript{MEng Broadcast Engineering}
\location{Distinction}
\sectionsep
\subsection{Assocation of Proj Mgmt}
\descript{Project Management Cert}
\location{APM-PMQ}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Languages:}
Java \textbullet{} Bash \textbullet{} Python \textbullet{} LaTeX\ \\ 
Matlab \textbullet{} C \textbullet{} C++ \textbullet{} SQL \\
\sectionsep

\subsection{Leadership}
\location{Interests \& Skills:}
Service Management \\
Workflow Improvement \\
Incident Management \\
Continuous Improvement \\
Effecting Culture Change \\
Mentoring/Coaching \\
Agile Methodology \\
Empowering \& Building Teams \\
\sectionsep

\subsection{Engineering}
\location{Interests \& Skills:}
Project Engineering \\
Requirements Assessment \\ 
Technical Documentation \\
IP Infrastructure \\
Broadcast Hardware \\
TV \& Radio Distribution \\
Broadcast Automation \\
Systems Integration \\
Control Systems Dev \\
Virtualisation Technologies \\
Monitoring Tools (Icinga/Nagios)\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Employment \& Voluntary Work}

\runsubsection{BBC}
\descript{| Project Manager / Senior Systems Engineer (2 Years)}
\location{Nov 2021 – Present | Glasgow, Scotland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Revitalisation of the News TV studio operations in BBC Scot, working into a programme of works spanning two years and £500k+ of investment.
\item Interview Champion - helping to change the BBC's interview culture and promote fair, inclusive hiring processes across the organisation.
\item Accountable for delivery of project tasks for myself and for the work of engineers reporting in to me during the project period.
\item Mentoring and supporting colleagues, leading ad-hoc teams where appropriate, and acting as a source of best practice within BBC Scotland.
\item Delivering strategic workflow \& cultural change, to improve cost-effectiveness and capability across TV, Radio \& Online production, as part of the Value For All and Digital First strategies.
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Operations Engineer (3 Years)}
\location{Jun 2018 – Nov 2021 | Glasgow, Scotland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Based in BBC Scot with Engineering Operations, supporting ops \& incident mgmt across TV, Radio and building \& facility infrastructure at sites across Scot.
\item Project work - worked to build new edit faciltiies at Dumbarton studios, VO booths in TV Presentation and upgrading DAW spaces in Pacific Quay.
\item Taken primary system ownership for supporting and developing a number of systems in BBC Scotland including the internal Raven ingest/playout system.
\item Worked with key industry suppliers and partners such as Grass Valley, Viz and VCS to find resolutions to incidents which require supplier intervention. 
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Project Manager (1 Year)}
\location{Jan 2020 – Jan 2021 | Glasgow, Scotland}
\begin{tightemize}
\item Managed the upgrade of the VCS radio prod \& playout system within Scotland, a multi-site, pan-BBC service upgrade - liasing between local prod teams, suppliers, and local \& national engineering support.
\item Other projects include managing the design, tender \& procurement of the £180k studio infrastructure upgrade across the 3 major Scottish TV studios.
\item Led a programme to change our documentation from the ground up - infosec approval of a new Password Manager, migrating to the BBC's "Confluence" managed service, \& developing our doc processes to match our support model.
\end{tightemize}
\sectionsep

\runsubsection{BBC}
\descript{| Trainee Broadcast Engineer (MEng) (2 Years)}
\location{Jul 2016 – May 2018 | Glasgow, Scotland}
\sectionsep

\runsubsection{BBC}
\descript{| Apprentice Broadcast Engineer (BEng) (3 Years)}
\location{Sep 2013 – Jul 2016 | Birmingham, England \& Glasgow, Scotland}
\begin{tightemize}
\item Worked for BBC English Regions \& BBC Scotland, including attachments to external organisations including Arqiva and STV.
%\item Worked as a 3rd line engineer for English Regions' testing and development team, including with the project team releasing ViLoR to English Regions
%\item Secondment to Arqiva \& changed the Radio 4 Long Wave antenna at Droitwich.
\item Worked across two UK General Elections, a Scottish GE and two referendums, as well as the Commonwealth Games in Glasgow.
\end{tightemize}
\sectionsep

\runsubsection{National Student Television Association (2 Years)}
\descript{| Executive Technical Officer \& Electoral Returning Officer }
\location{Jul 2012 – Jul 2015 | UK Nationwide}
\begin{tightemize}
\item Elected \& re-elected for two terms of office.
\item Honoured at the end with a term as the association's Returning Officer.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}
